Ensemble labels

### 2021-01-26 docs/ensemble_labels.Rmd
Move to a new method to select ensemble labels

```{r}
library(tidyr)
library(parallel)
# Define the width of chips to cut
# In this case, 256 *256 chip.
width_chips <- 16
lc_labels <- rast('data/intermid/lc_labels_exd_val.tif')
tiles <- st_read('data/geoms/tiles_nicfi.geojson',
                 quiet = T) %>% dplyr::select(tile)
tiles <- do.call(rbind, mclapply(1:nrow(tiles), function(n){
  tile <- tiles %>% slice(n)
  tiles_grids <- st_make_grid(tile, n = c(width_chips, width_chips)) %>% 
    st_sf() %>% arrange() %>% 
    mutate(tile = tile$tile,
                       index = c(1:(width_chips^2)))
}, mc.cores = 12))
st_write(tiles, 'data/intermid/tiles_grids_256.geojson')
tiles <- tiles %>% vect()

@@

labels_sum <- labels_sum %>% filter(count > 0)
tiles_grids_selected <- do.call(rbind, 
                                lapply(labels_sum$name, 
                                       function(nm){
    message(nm)
    if (nm %in% c('Forest', 'Grassland', 'Cropland', 'Shrubland')){
        set.seed(123)
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, nm) %>% 
            # arrange_at(nm, funs(desc)) %>% 
            filter(!is.na(!!rlang::sym(nm))) %>% 
            filter((!!rlang::sym(nm)) >= 0.7) %>% 
            sample_n(min(1000, nrow(.)))
    } else if (nm == 'Water'){
        set.seed(566)
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, nm) %>% 
            # arrange_at(nm, funs(desc)) %>% 
            filter(!is.na(!!rlang::sym(nm))) %>%
            filter((!!rlang::sym(nm)) <= 0.8) %>%
            filter((!!rlang::sym(nm)) >= 0.4) %>% 
            sample_n(500)
    } else {
        # Bare land, wetland, and urban are classes that are hard to tell,
        # and the ensemble labels are less,
        # so we keep as many samples as possible.
        # but also if there are too few labels within a grid,
        # we assume the labels are not reliable anymore.
        # So we use a threshold 0.1.
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, all_of(nm)) %>%
            filter(!is.na(!!rlang::sym(nm))) %>%
            filter((!!rlang::sym(nm)) > 0.1)
    }
    data.frame(name = nm, 
               tile = tile_select$tile, 
               index = tile_select$index)
}))
```

>>>>

```{r}
library(ggplot2)
library(tidyr)
library(parallel)
# Define the width of chips to cut
# In this case, 256 * 256 chip.
# The chip size is the trade-off between computing cost, 
# purity of ensemble labels, and the keep of geographic context.
width_chips <- 16
lc_labels <- rast('data/intermid/lc_labels_exd_val.tif')
tiles <- st_read('data/geoms/tiles_nicfi.geojson',
                 quiet = T) %>% dplyr::select(tile)
tiles <- do.call(rbind, mclapply(1:nrow(tiles), function(n){
  tile <- tiles %>% slice(n)
  tiles_grids <- st_make_grid(tile, n = c(width_chips, width_chips)) %>% 
    st_sf() %>% arrange() %>% 
    mutate(tile = tile$tile,
                       index = c(1:(width_chips^2)))
}, mc.cores = 12))
st_write(tiles, 'data/intermid/tiles_grids_256.geojson')
tiles <- tiles %>% vect()

@@

labels_sum <- labels_sum %>% filter(count > 0)
tiles_grids_pure <- do.call(rbind, 
                            lapply(labels_sum$name, 
                                   function(nm){
    message(nm)
    tile_select <- tiles_labels %>% 
        dplyr::select(tile, index, all_of(nm)) %>% 
        filter(!is.na(!!rlang::sym(nm))) %>% 
        filter((!!rlang::sym(nm)) >= 0.8)
    data.frame(name = nm, 
               tile = tile_select$tile, 
               index = tile_select$index)
}))

grids_pure_count <- tiles_grids_pure %>% 
  group_by(name) %>% summarize(n = n()) %>% 
  arrange(n)
```

```{r, eval=T, echo=F, message=F, warning=F}
grids_pure_count <- read.csv('data/intermid/pure_grids_count.csv',
                             stringsAsFactors = F)

# Based on the table, the first three minor classes 
grids_pure_count %>%
  kbl(caption = "Pure label grids summary") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

Based on the table, the first three minor classes (`r grids_pure_count$name[1:3]`) have the similar number of pure grids. So we keep all grids from these classes, and then randomly select the average number (`r ceiling(mean(grids_pure_count$n[1:3]))`) of grids from other classes.

##### [ARCHIVED] Get large amount of weak labels.
Based on the prior experiments, this method didn't do well. The train dataset is "under-representative" in terms of DL training (Validate loss curve is below the train loss significantly). This might be caused by either the super imbalance in both train and validate dataset, or the noises in the labels.

```{r old-method}
labels_sum <- labels_sum %>% filter(count > 0)
tiles_grids_selected <- do.call(rbind, 
                                lapply(labels_sum$name, 
                                       function(nm){
    message(nm)
    if (nm %in% c('Forest', 'Grassland', 'Cropland', 'Shrubland')){
        set.seed(123)
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, nm) %>% 
            # arrange_at(nm, funs(desc)) %>% 
            filter(!is.na(!!rlang::sym(nm))) %>% 
            filter((!!rlang::sym(nm)) >= 0.7) %>% 
            sample_n(min(1000, nrow(.)))
    } else if (nm == 'Water'){
        set.seed(566)
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, nm) %>% 
            # arrange_at(nm, funs(desc)) %>% 
            filter(!is.na(!!rlang::sym(nm))) %>%
            filter((!!rlang::sym(nm)) <= 0.8) %>%
            filter((!!rlang::sym(nm)) >= 0.4) %>% 
            sample_n(500)
    } else {
        # Bare land, wetland, and urban are classes that are hard to tell,
        # and the ensemble labels are less,
        # so we keep as many samples as possible.
        # but also if there are too few labels within a grid,
        # we assume the labels are not reliable anymore.
        # So we use a threshold 0.1.
        tile_select <- tiles_labels %>% 
            dplyr::select(tile, index, all_of(nm)) %>%
            filter(!is.na(!!rlang::sym(nm))) %>%
            filter((!!rlang::sym(nm)) > 0.1)
    }
    data.frame(name = nm, 
               tile = tile_select$tile, 
               index = tile_select$index)
}))
```
